\documentclass[9pt, a4paper]{article}

\usepackage{geometry}
\geometry{a4paper, margin=0.5in, bottom=0.75in}
\usepackage{wallpaper}
\usepackage[hidelinks]{hyperref}
\usepackage{paracol}

% Do not indent paragraphs
\setlength\parindent{0in}

% \pagenumbering{gobble} does not work in this case.
% Likely due to the code for the lines needing page reference numbers.
% We use fancyhdr to modify it instead.
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt} % Prevent top line from appearing
\rfoot{\footnotesize Page \thepage \hspace{1pt} of \pageref{LastPage}} % Format of the page numbers
% \rfoot{} % Format of the page numbers

\usepackage{multicol}
% \usepackage{ragged2e}



% TYPOGRAPHY
%--------------------------------
\usepackage{fontspec} 
\usepackage{fontawesome5}
\usepackage{xunicode}
\usepackage{xltxtra}
% converts LaTeX specials (quotes, dashes etc.) to Unicode
\defaultfontfeatures{LetterSpace=-4}
%\defaultfontfeatures{Mapping=tex-text}
\setmainfont[Ligatures={Common}, BoldFont={Inter Semi Bold}]{Inter}
% Cool ampersand
\newcommand{\amper}{{\fontspec[Scale=.95]{Inter}\selectfont\itshape\&}}
\usepackage{setspace}
\usepackage[inline]{enumitem}

\newcommand{\middot}{~\textperiodcentered~}

\setlist[itemize]{leftmargin=*} % removes margin from the itemize

\newlist{hlist}{itemize*}{1}
\setlist[hlist]{label={}, afterlabel={}, mode=unboxed,
itemjoin=\discretionary{}{}{\hbox{\middot}}}

\usepackage{lipsum,xcolor}
\newcommand\dunderline[3][-1pt]{{%
\sbox0{#3}%
\ooalign{\copy0\cr\rule[\dimexpr#1-#2\relax]{\wd0}{#2}}}}

% LANGUAGE
%--------------------------------
% Set the main language for formatting purposes, just in case.
\usepackage{polyglossia}
\setmainlanguage{en-GB}


% LINES BETWEEN ITEMS
%--------------------------------
\usepackage{tikz,tikzpagenodes}
\usetikzlibrary{calc}
\usepackage{refcount}

\newcounter{mylist} % new counter for amount of lists
\newcounter{mycnt}[mylist] % create new item counter
\newcounter{mytmp}[mylist] % tmp counter needed for checking before/after current item

\newcommand{\drawoptionsconn}{black, shorten <= .5mm, shorten >= .5mm, thick}
\newcommand{\drawoptionsshort}{black, shorten <= .5mm, shorten >= -1mm, thick}

\newcommand{\myitem}{% Modified `\item` to update counter and save nodes
	\stepcounter{mycnt}%
	\item[\linkedlist{%
		i\alph{mylist}\arabic{mycnt}}]%
	\label{item-\alph{mylist}\arabic{mycnt}}%
	\ifnum\value{mycnt}>1%
	\ifnum\getpagerefnumber{item-\alph{mylist}\arabic{mytmp}}<\getpagerefnumber{item-\alph{mylist}\arabic{mycnt}}%
	\begin{tikzpicture}[remember picture,overlay]%
		\expandafter\draw\expandafter[\drawoptionsshort] (i\alph{mylist}\arabic{mycnt}) --
		++(0,3mm) --
		(i\alph{mylist}\arabic{mycnt} |- current page text area.north);% draw short line
	\end{tikzpicture}%
	\else%
	\begin{tikzpicture}[remember picture,overlay]%
		\expandafter\draw\expandafter[\drawoptionsconn] (i\alph{mylist}\arabic{mytmp}) -- (i\alph{mylist}\arabic{mycnt});% draw the connecting lines
	\end{tikzpicture}%
	\fi%
	\fi%
	\addtocounter{mytmp}{2}%
	\IfRefUndefinedExpandable{item-\alph{mylist}\arabic{mytmp}}{}{% defined
		\ifnum\getpagerefnumber{item-\alph{mylist}\arabic{mytmp}}>\getpagerefnumber{item-\alph{mylist}\arabic{mycnt}}%
		\begin{tikzpicture}[remember picture,overlay]%
			\expandafter\draw\expandafter[\drawoptionsshort] (i\alph{mylist}\arabic{mycnt}) --
			++(0,-3mm) --
			(i\alph{mylist}\arabic{mycnt} |- current page text area.south);% draw short line
		\end{tikzpicture}%
		\fi%
	}%
	\addtocounter{mytmp}{-1}%
}

\newcommand{\linkedlist}[1]{
	\raisebox{1.5pt}[0pt][0pt]{\begin{tikzpicture}[remember picture]%
			\node (#1) [black,circle,fill,inner sep=1.5pt]{};
	\end{tikzpicture}}%
}

\newenvironment{myitemize}{%
	% Create new `myitemize` environment to keep track of the counters
	\stepcounter{mylist}% increment list counter
	\begin{itemize}
	}{\end{itemize}%
}

\newcommand{\titleheader}[1]{{\defaultfontfeatures{LetterSpace=0}\setmainfont{Futura} \textcolor{black} {\huge\textbf{#1}\vspace{2pt}}}}
\newcommand{\heading}[1]{{\defaultfontfeatures{LetterSpace=0}\setmainfont{Futura} \textcolor{black} {\dunderline[-3pt]{2pt}{\small \textbf{#1}}}}}
\newcommand{\itemheading}[1]{{\defaultfontfeatures{LetterSpace=-2}\setmainfont{Futura} \small \textbf{#1}}}
\newcommand{\subheading}[1]{{\defaultfontfeatures{LetterSpace=-3}\setmainfont{Futura} \small \textit{#1}}}
\newcommand{\monthyear}[1]{{\defaultfontfeatures{LetterSpace=-3}\setmainfont{Futura} \small #1}}
\newcommand{\motto}[1]{{\defaultfontfeatures{LetterSpace=-3}\setmainfont{Futura} \small #1}}

\hypersetup{
pdftitle={Vincent Leonardo's Curriculum Vitae},
pdfsubject={Curriculum Vitae},
pdfauthor={Vincent Leonardo},
}


\begin{document}
\columnratio{0.8}

\titleheader{VINCENT LEONARDO}\\
\motto{Aspiring AI engineer and front end developer}
\smallbreak

\begin{hlist}
	{ \footnotesize 
				\item +65 8817 0611
		
				\item \href{mailto:vincent@vinleonardo.com}{vincent@vinleonardo.com}
		
				\item \href{https://vinleonardo.com}{vinleonardo.com}
		
				\item \href{https://github.com/vincentleooo/}{\faGithub\ vincentleooo}
		
				\item \href{https://www.linkedin.com/in/vincentleoooo/}{\faLinkedin\ vincentleoooo}
			}
\end{hlist}

\vspace{0.2in}

\heading{ABOUT}
\medbreak
\vspace{1pt}
{\small A keen and passionate learner obsessed with anything technology
related. Currently seeking a career in building models using machine
learning or deep learning to assess and make decisions to make the world
a better place. Particular in crafting tools and interfaces to allow for
easier usage of prediction models and data visualisation.
Multidisciplinary, with expertise in data science, system
administration, and computer hardware as well. Enjoys collaborative work
and creative problem-solving.}

\vspace{0.2in}

\heading{EDUCATION}
\smallbreak
\vspace{2pt}
\begin{myitemize}[topsep=0ex, labelsep=0.1in]
		\begin{paracol}{2}\myitem\itemheading{Singapore University of
Technology and Design}\\\subheading{Bachelor of Engineering with Honours
(Engineering Systems and
Design)}\switchcolumn{\vspace*{5pt}\small\monthyear{Singapore}\\\monthyear{May
2019 -- Present}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Expected to graduate in September 2022.}
				\item {\small Focusing on Artificial Intelligence-related courses
and applications.}
				\item {\small Awarded with the SUTD Undergraduate Merit
Scholarship.}
			\end{itemize}
	\end{myitemize}

\vspace{0.16in}

\heading{EXPERIENCE}
\smallbreak
\vspace{2pt}
\begin{myitemize}[topsep=0ex, labelsep=0.1in]
		\begin{paracol}{2}\myitem\itemheading{What Is Up,
Indonesia?}\\\subheading{Newsletter Writer \& Web
Developer}\switchcolumn{\vspace*{5pt}\monthyear{Singapore}\\\monthyear{May
2022 -- Present}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Working alongside three other team members on weekly
email newsletters discussing Indonesian news headlines in English that
reaches over 500 people.}
				\item {\small Writing and maintaining their website
(\href{https://whatisupindonesia.com}{whatisupindonesia.com}) using
Next.js (React) with MDX templates.}
				\item {\small Exploring content management systems to implement on
the website complementing the main
\href{https://www.instagram.com/whatisupindonesia/}{Instagram} page.}
			\end{itemize}
		\begin{paracol}{2}\myitem\itemheading{Silver Online
Service}\\\subheading{Marketing
Coordinator}\switchcolumn{\vspace*{5pt}\monthyear{Singapore}\\\monthyear{May
2022 -- Present}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Advising for the creation of the company's brand
identity and design for Instagram posts and the website.}
				\item {\small Developing a landing page website to increase reach.}
			\end{itemize}
		\begin{paracol}{2}\myitem\itemheading{SUTD Humanities, Arts and Social
Sciences}\\\subheading{Web Designer \&
Developer}\switchcolumn{\vspace*{5pt}\monthyear{Singapore}\\\monthyear{May
2022 -- Present}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Designing the UI/UX to house film archives
complementing Prof Sandeep Ray's book, \textit{Celluloid Colony}.}
				\item {\small Developing a React-based website that links to a
database containing these archives.}
			\end{itemize}
		\begin{paracol}{2}\myitem\itemheading{Shopee Pte
Ltd}\\\subheading{Regional Operations (Fraud)
Intern}\switchcolumn{\vspace*{5pt}\monthyear{Singapore}\\\monthyear{May
2021 -- Sep 2021}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Wrangled and examined large user behaviour datasets
using Python and SQL.}
				\item {\small Ideated rules that reduce instances of fraud along
with their impact analyses with three other departments.}
			\end{itemize}
		\begin{paracol}{2}\myitem\itemheading{SUTD DManD
Centre}\\\subheading{Composites Research
Intern}\switchcolumn{\vspace*{5pt}\monthyear{Singapore}\\\monthyear{May
2020 -- Sep 2020}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Optimised composites manufacturing processes and
scripted automated simulations using ANSYS.}
				\item {\small Spearheaded computer equipment purchasing decisions,
saving about 30--40\% of the team's budget compared to initial plans.}
			\end{itemize}
	\end{myitemize}

\vspace{0.16in}

\heading{COMPETITIONS}
\smallbreak
\vspace{2pt}
\begin{myitemize}[topsep=0pt, labelsep=0.1in]
		\begin{paracol}{2}\myitem\itemheading{\href{https://github.com/vincentleooo/analytics-edge-data-comp}{The Analytics Edge Data Competition}}\\\subheading{SUTD
40.016 The Analytics
Edge}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Nov 2021 --
Dec 2021}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Headed the team of two to clinch first place in terms
of accuracy amongst the cohort.}
				\item {\small Applied the RoBERTa model in TensorFlow in R to secure
around 96\% accuracy in the sentiment classification task.}
			\end{itemize}
		\begin{paracol}{2}\myitem\itemheading{\href{https://vinleonardo.com/synthesis-sustainable-competition-2021/}{Synthesis Sustainability IRL Data Challenge}}\\\subheading{Synthesis
\& Treatsure}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Oct
2021 -- Nov 2021}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Directed the team of three to win third place in the
data science challenge among around 135 participants.}
				\item {\small Modelled word associations and sentiments on food
surplus consumption from Twitter and Instagram posts in the past five
years to consult Treatsure on persuading more people to consume surplus
food.}
			\end{itemize}
	\end{myitemize}

\vspace{0.16in}

\heading{PROJECTS}
\smallbreak
\vspace{2pt}
\begin{myitemize}[topsep=0pt, labelsep=0.1in]
		\begin{paracol}{2}\myitem\itemheading{Gait Recognition Model and
Analytics}\\\subheading{Klass Engineering Pte
Ltd}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Jan 2022 --
Present}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Leading a team of five from two different pillars to
model unique identification of people based on their gait alone.}
				\item {\small Synthesising a pipeline from video feed to
classification using React, FastAPI, OpenCV, and OpenGait models.}
			\end{itemize}
		\begin{paracol}{2}\myitem\itemheading{Music Genre
Classification}\\\subheading{SUTD 50.039 Theory and Application of Deep
Learning}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Jan 2022
-- May 2022}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Crafted a lightweight parallel CNN model to classify
music genres using the GTZAN dataset to achieve around 80\% accuracy.}
				\item {\small Split inputs into three-second chunks, and ensembling
predictions based on these chunks for unseen data of any length.}
				\item {\small Created a simple CLI application and a prototype web
interface for ease-of-use.}
			\end{itemize}
		\begin{paracol}{2}\myitem\itemheading{\href{https://github.com/vincentleooo/CDS-Project-2021}{Classification of MBTI Type Based on Past Posts on Internet Forums}}\\\subheading{SUTD
50.038 Computational Data
Science}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Oct 2021
-- Dec 2021}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Devised model to predict the MBTI of the
PersonalityCafe forum users based on their posts within the team of
three.}
				\item {\small Merged a CNN with an LSTM using PyTorch after
experimentations involving SVM, logistic regression, decision trees,
ensemble models, and neural networks in order to achieve an accuracy of
78\% for the top six classes.}
			\end{itemize}
		\begin{paracol}{2}\myitem\itemheading{\href{https://github.vinleonardo.com/sma-airport-model/}{Agent-Based Modelling for Airport Arrivals in a Post-Pandemic World}}\\\subheading{SUTD
40.015 Simulations Modelling
Analysis}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Oct 2021
-- Dec 2021}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Project highlighted for the course in the
\href{https://esd.sutd.edu.sg/files/ESD-Spring-Newsletter-2022.pdf}{ESD pillar newsletter}
in early 2022.}
				\item {\small Managed the team of three in designing the
architecture and user experience of the simulation using d3.js.}
			\end{itemize}
		\begin{paracol}{2}\myitem\itemheading{Optimisation of Pre-Surgery
Assessment Appointment Slots}\\\subheading{Singapore General Hospital
Pre-Admission
Centre}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Mar 2021
-- May 2021}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Partnered with client to gather and clean the
appointment data over the past three years to form statistical
inferences in R.}
				\item {\small Collaborated with team of four to implement the M/M/s
on Excel to optimise manpower, queue time, and working hours.}
			\end{itemize}
		\begin{paracol}{2}\myitem\itemheading{Analysis of Carsharing Usage
Pattern and Utilisation}\\\subheading{Car Club Pte
Ltd}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Sep 2020 --
Dec 2020}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Guided a team of four to analyse the effects of
COVID-19 on carsharing usage using tools such as R, SQL, Python and
GIS.}
				\item {\small Wrote Python scripts to automate the sifting and
analysis of four months of customer data provided in Excel format.}
				\item {\small Consulted the industry partner (Car Club) on possible
measures on adapting to the new behaviours found due to COVID-19.}
			\end{itemize}
	\end{myitemize}

\vspace{0.16in}

\heading{TEACHING EXPERIENCE}
\smallbreak
\vspace{2pt}
\begin{myitemize}[topsep=0pt, labelsep=0.1in]
		\begin{paracol}{2}\myitem\itemheading{60.002 AI Applications in
Design}\\\subheading{Teaching
Assistant}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Jan
2022 -- May 2022}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Guided students in both technical aspects and design
thinking using Fusion360's generative design feature.}
				\item {\small Mentored groups in their projects involving web
scraping and text analysis using various Python packages.}
				\item {\small Taught Python and TensorFlow installation and
debugging skills.}
			\end{itemize}
		\begin{paracol}{2}\myitem\itemheading{10.020 Data Driven
World}\\\subheading{Teaching
Assistant}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Sep
2021 -- Dec 2021}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Tutored students in all the course concepts,
especially in recursive concepts and data wrangling.}
				\item {\small Taught students generalisable debugging and
problem-solving skills.}
			\end{itemize}
	\end{myitemize}

\vspace{0.16in}

\heading{ACADEMIC PROJECTS}
\smallbreak
\vspace{2pt}
\begin{myitemize}[topsep=0pt, labelsep=0.1in]
		\begin{paracol}{2}\myitem\itemheading{Reducing Composites Wastage
Through Custom Vacuum Bag Sealing}\\\subheading{Undergraduate Research
Opportunities Programme
(UROP)}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Sep 2020
-- Dec 2020}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Assisted in the prototypes and experiments using
smaller and reusable custom vacuum bags for composites fabrication.}
				\item {\small Conducted IT equipment maintenance and debugging for
the research team.}
			\end{itemize}
		\begin{paracol}{2}\myitem\itemheading{Design and Fabrication of a
Toggling Speaker-Microphone (Phase 3)}\\\subheading{Undergraduate
Research Opportunities Programme
(UROP)}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Sep 2019
-- May 2020}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Assisted in the design and 3D printing of prototypes
for the cones and speakers.}
				\item {\small Analysed frequency response of the signals produced
using different cones and speakers.}
			\end{itemize}
	\end{myitemize}

\vspace{0.16in}
\newpage

\heading{CO-CURRICULAR ACTIVITIES}
\smallbreak
\vspace{2pt}
\begin{myitemize}[topsep=0pt, labelsep=0.1in]
		\begin{paracol}{2}\myitem\itemheading{SUTD Photographic
Circle}\\\subheading{Chief Photographer (Previously Treasurer, 2019 --
2021)}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Feb 2021 --
Feb 2022}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Oversaw the standards of the photographs sent to the
clients over five major events.}
				\item {\small Spearheaded a film development workshop that was fully
booked within one hour.}
			\end{itemize}
		\begin{paracol}{2}\myitem\itemheading{SUTD 9th Student
Government}\\\subheading{Advisor, Media \& Marketing (Previously
Director of Creative Media, 2019 --
2020)}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Nov 2020 --
Feb 2022}}\end{paracol}
	\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
				\item {\small Advised and assisted the Media \& Marketing team of
seven on student engagement projects in the university.}
				\item {\small Co-led the Mental Health Awareness Week initiative,
reaching over 1000 people through videos and Telegram Stickers.}
			\end{itemize}
	\end{myitemize}

\vspace{0.16in}


\vspace*{0.2in}

\heading{ADDITIONAL INFORMATION}
\begin{itemize}[itemsep=-0.4ex]
		\item {\small Native English and Bahasa Indonesia speaker.}
		\item {\small Comfortable in Linux/Unix-based systems and shell
scripting, especially in web servers and for deep learning purposes.}
		\item {\small Comfortable in maintaining, customising, and upgrading
computers.}
		\item {\small Participated in the Create4Good Innovation Fund Social
Venture Programme as part of Silver Online Service, a social venture to
help the elderly adapt to modern technology, and was awarded \$50,000 in
funding for the project.}
		\item {\small Contributed to the Temasek Foundation-National
University of Singapore Leadership Enrichment and Regional Networking
Young Asian Leaders Initiative (2021).}
		\item {\small Enjoys history, linguistics, music, and tinkering with
technology to automate various things, including this CV.}
	\end{itemize}

\end{document}